Pancreatic endocrinogenesis

### 2024-07-31 nbs/tutorials/pancreas/pancreas.qmd
feat(nbs): add support for model comparison to pancreas notebook
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

Please see the [guide on interactive results review](/guides/interactive/interactive.qmd) for a 
general review of how to download and review results. Here we use the same 
approach without any of the explanatory text to retrieve model results to 
generate plots for model selection and evaluation

@@

### Setup remote connection

```{python}
#| label: instantiate-remote-client
from flytekit.remote.remote import FlyteRemote
from flytekit.configuration import Config

remote = FlyteRemote(
    Config.for_endpoint("flyte.cluster.pyrovelocity.net"),
)
```

@@

```{python}
# | label: get-workflow-io
workflow_inputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a/f26c1pjy-0-dn1-0-dn6/i"
)
postprocessing_outputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a/f26c1pjy-0-dn1-0-dn6/o"
)
```

```{python}
# | label: create-outputs-dict
from omegaconf import OmegaConf
from flytekit.interaction.string_literals import literal_map_string_repr
from pyrovelocity.utils import print_config_tree

inputs_dict = literal_map_string_repr(workflow_inputs.literals)
inputs_dictconfig = OmegaConf.create(inputs_dict)
print_config_tree(inputs_dict)

outputs_dict = literal_map_string_repr(postprocessing_outputs.literals)
outputs_dictconfig = OmegaConf.create(outputs_dict)
print_config_tree(outputs_dict)
```

@@

```{python}
#| label: download-outputs
from pyrovelocity.io.gcs import download_blob_from_uri

pyrovelocity_data = download_blob_from_uri(
    outputs_dictconfig.o0.pyrovelocity_data.path
)
postprocessed_data = download_blob_from_uri(
    outputs_dictconfig.o0.postprocessed_data.path
)
```

@@

### Load data

```{python}
# | label: load-postprocessed-data
# | output: true
import scanpy as sc
from pyrovelocity.utils import print_anndata

adata = sc.read(postprocessed_data)
print_anndata(adata)
```

```{python}
# | label: load-posterior-samples
# | output: true
from pyrovelocity.utils import pretty_print_dict
from pyrovelocity.io import CompressedPickle

posterior_samples = CompressedPickle.load(pyrovelocity_data)
pretty_print_dict(posterior_samples)
```

### Extract results of interest

```{python}
# | label: extract-gene-selection
from pyrovelocity.analysis.analyze import pareto_frontier_genes

@@

### Generate plots

```{python}
# | label: generate-gene-selection-summary-plot
# | output: false
from pyrovelocity.plots import plot_gene_selection_summary

vector_field_basis = inputs_dictconfig.preprocess_data_args.vector_field_basis
cell_state = inputs_dictconfig.preprocess_data_args.cell_state

@@

```{python}
# | label: show-gene-selection-summary-plot
# | code-fold: true
# | output: true
display(Image(filename=f"gene_selection_summary_plot.pdf.png"))
```

>>>>

Please see the [guide on interactive results review](/guides/interactive/interactive.qmd) for a 
general review of how to download and review results. Here we use the same 
approach without any of the explanatory text to retrieve model results to 
generate plots for model selection and evaluation.

@@

@@

```{python}
# | label: get-workflow-io
from pyrovelocity.io.cluster import get_remote_task_results

(
    model1_postprocessing_inputs,
    model1_postprocessing_outputs,
) = get_remote_task_results(
    execution_id="pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a",
    task_id="f26c1pjy-0-dn1-0-dn3",
)

(
    model2_postprocessing_inputs,
    model2_postprocessing_outputs,
) = get_remote_task_results(
    execution_id="pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a",
    task_id="f26c1pjy-0-dn1-0-dn6",
)
```

@@

```{python}
# | label: download-outputs
from pyrovelocity.io.gcs import download_blob_from_uri

model1_pyrovelocity_data = download_blob_from_uri(
    blob_uri=model1_postprocessing_outputs.o0.pyrovelocity_data.path,
    download_filename_prefix=f"{model1_postprocessing_inputs.training_outputs.data_model}",
)
model1_postprocessed_data = download_blob_from_uri(
    blob_uri=model1_postprocessing_outputs.o0.postprocessed_data.path,
    download_filename_prefix=f"{model1_postprocessing_inputs.training_outputs.data_model}",
)

model2_pyrovelocity_data = download_blob_from_uri(
    blob_uri=model2_postprocessing_outputs.o0.pyrovelocity_data.path,
    download_filename_prefix=f"{model2_postprocessing_inputs.training_outputs.data_model}",
)
model2_postprocessed_data = download_blob_from_uri(
    blob_uri=model2_postprocessing_outputs.o0.postprocessed_data.path,
    download_filename_prefix=f"{model2_postprocessing_inputs.training_outputs.data_model}",
)
```

@@

### Model 1

#### Load data

```{python}
# | label: model1-load-postprocessed-data
# | output: true
import scanpy as sc
from pyrovelocity.utils import print_anndata

adata = sc.read(model1_postprocessed_data)
print_anndata(adata)
```

```{python}
# | label: model1-load-posterior-samples
# | output: true
from pyrovelocity.utils import pretty_print_dict
from pyrovelocity.io import CompressedPickle

posterior_samples = CompressedPickle.load(model1_pyrovelocity_data)
pretty_print_dict(posterior_samples)
```

#### Extract results of interest

```{python}
# | label: model1-extract-gene-selection
from pyrovelocity.analysis.analyze import pareto_frontier_genes

@@

#### Generate plots

```{python}
# | label: model1-generate-gene-selection-summary-plot
# | output: false
from pyrovelocity.plots import plot_gene_selection_summary

vector_field_basis = model1_postprocessing_inputs.preprocess_data_args.vector_field_basis
cell_state = model1_postprocessing_inputs.preprocess_data_args.cell_state

@@

```{python}
# | label: model1-show-gene-selection-summary-plot
# | code-fold: true
# | output: true
display(Image(filename=f"gene_selection_summary_plot.pdf.png"))
```

### Model 2

#### Load data

```{python}
# | label: model2-load-postprocessed-data
# | output: true
import scanpy as sc
from pyrovelocity.utils import print_anndata

adata = sc.read(model2_postprocessed_data)
print_anndata(adata)
```

```{python}
# | label: model2-load-posterior-samples
# | output: true
from pyrovelocity.utils import pretty_print_dict
from pyrovelocity.io import CompressedPickle

posterior_samples = CompressedPickle.load(model2_pyrovelocity_data)
pretty_print_dict(posterior_samples)
```

#### Extract results of interest

```{python}
# | label: model2-extract-gene-selection
from pyrovelocity.analysis.analyze import pareto_frontier_genes

#### Generate plots

```{python}
# | label: model2-generate-gene-selection-summary-plot
# | output: false
from pyrovelocity.plots import plot_gene_selection_summary

vector_field_basis = model2_postprocessing_inputs.preprocess_data_args.vector_field_basis
cell_state = model2_postprocessing_inputs.preprocess_data_args.cell_state

```{python}
# | label: model2-show-gene-selection-summary-plot
# | code-fold: true
# | output: true
display(Image(filename=f"gene_selection_summary_plot.pdf.png"))
```
